---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(sqlr.template)
```

# sqlr.template

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/gipso/sqlr.template/workflows/R-CMD-check/badge.svg)](https://github.com/gipso/sqlr.template/actions)
[![Codecov test coverage](https://codecov.io/gh/gipso/sqlr.template/branch/main/graph/badge.svg)](https://app.codecov.io/gh/gipso/sqlr.template?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

## Overview

> This is a template repository for systematic quantitative literature reviews (SQLR) research compendiums.

`sqlr.template` is an R package with the research compendium of the Interdisciplinary Sleep Research Group (GIPSO) [INSERT THE NAME OF THE PROJECT] systematic quantitative literature review. The aim of `sqlr.template` is to facilitate the research work, in addition to contributing to the reproducibility of the research.

The assemble of this package was inspired by Ben Marwick, Carl Boettiger & Lincoln Mullen's article ["Packaging Data Analytical Work Reproducibly Using R (and Friends)"](https://doi.org/10.1080/00031305.2017.1375986).

Learn more about systematic quantitative literature reviews (SQLR) [here](https://www.griffith.edu.au/griffith-sciences/school-environment-science/research/systematic-quantitative-literature-review).

## Installation

You can install `sqlr.template` from GitHub with:

``` {r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("gipso/sqlr.template")
```

We don’t intend to publish this package to CRAN.

## Citation

If you use `sqlr.template` in your research, please consider citing it. We put a lot of work to build and maintain a free and open-source R package. You can find the `sqlr.template` citation below.

```{r}
citation("sqlr.template")
```
